\documentclass[12pt]{article}

% ==================================================
% Journal of Regional Science (JRS) submission-oriented main file
% Blinded submission by default. Set \blindfalse for a personal draft.
% ==================================================
\newif\ifblind
\blindtrue
% \blindfalse

% ---------- Packages ----------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\IfFileExists{newtxtext.sty}{
  \IfFileExists{binhex.tex}{
    \usepackage{newtxtext,newtxmath}
  }{
    \IfFileExists{mathptmx.sty}{
      \usepackage{mathptmx}
    }{
      \IfFileExists{lmodern.sty}{\usepackage{lmodern}}{}
    }
  }
}{
  \IfFileExists{mathptmx.sty}{
    \usepackage{mathptmx}
  }{
    \IfFileExists{lmodern.sty}{\usepackage{lmodern}}{}
  }
}
\usepackage[authoryear]{natbib}
\bibpunct{(}{)}{;}{a}{,}{,}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\let\openbox\relax
\usepackage{amsmath,amsthm,mathtools}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{array}
\usepackage{enumitem}
\usepackage{xurl}
\usepackage{url}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{hyperref}
\usetikzlibrary{arrows.meta,positioning,calc,patterns}
\usepgfplotslibrary{fillbetween}
\pgfplotsset{compat=1.18}

% ---------- Layout ----------
\onehalfspacing
\setlength{\parskip}{0.35em}
\setlength{\parindent}{1.25em}
\raggedbottom
\hbadness=10000
\vbadness=10000

\pagestyle{plain}

% ---------- Theorem environments ----------
\theoremstyle{plain}
\newtheorem{assumption}{Assumption}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{theorem}{Theorem}
\theoremstyle{remark}
\newtheorem{remark}{Remark}
\newtheorem*{definition}{Definition}

% ---------- Metadata ----------
\newcommand{\papertitle}{Public Co-Creation Hubs, Cross-Regional Pipelines, and Dynamic Efficiency in Thin Regional Ecosystems}
\newcommand{\articletype}{Original Article}
\newcommand{\shorttitle}{Public Hubs and Cross-Regional Pipelines}
\newcommand{\authorname}{Ryota Matsuki}
\newcommand{\authoraffil}{Independent Researcher, Matsuyama, Ehime, Japan}
\newcommand{\authoremail}{ryota.matsuki@gmail.com}
\newcommand{\JELcodes}{H70, O31, O38, R11, R12, R58}
\newcommand{\keywordslist}{public co-creation hubs; cross-regional pipelines; regional innovation; place-based policy; local buzz; lock-in; thin regional ecosystems}

\hypersetup{
  pdftitle={\papertitle},
  pdfsubject={Journal of Regional Science submission manuscript},
  pdfauthor={\ifblind Anonymous\else \authorname\fi},
  pdfkeywords={\keywordslist},
  colorlinks=true,
  linkcolor=black,
  citecolor=black,
  urlcolor=blue
}

% ---------- Title ----------
\title{\papertitle}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{plain}

\ifblind
\begin{center}
\normalsize
\emph{Author information omitted for double-blind review.}
\end{center}
\vspace{0.6em}
\else
\begin{center}
\normalsize
\authorname\\
\authoraffil\\
E-mail: \href{mailto:\authoremail}{\authoremail}
\end{center}
\vspace{0.6em}
\fi

\noindent\textbf{Abstract}

\noindent
Local governments increasingly support co-creation hubs, enterprise hubs, and related collaborative spaces as place-based instruments for strengthening regional innovation. Yet the welfare case for such interventions is unclear in thin regional ecosystems, where the local participant pool is limited and repeated local interaction may quickly become redundant. This paper develops a two-region, two-period model in which a public hub raises local matching within a target region, while a complementary pipeline policy creates cross-regional renewal through outside linkages. The analysis yields three main results. First, a hub is socially efficient only if its local coordination gains are large enough to offset fixed cost and the dynamic redundancy generated by repeated local interaction. Second, short-run success and social efficiency are not equivalent: a hub may appear attractive under visible first-period activity metrics while being socially undesirable once dynamic novelty loss is taken into account. Third, the relevant policy object is often not a hub alone but a policy bundle combining local coordination with cross-regional pipeline formation. A hub that fails as a stand-alone intervention may become socially efficient when paired with sufficiently effective outside-linkage policy. Extensions show that participant composition strengthens the case for hub policy, while digital coordination technologies weaken the case for physical hub creation when they substitute for baseline local matching. The model also generates empirically testable predictions on repeated ties, outside collaboration, and absorptive capacity. The results suggest that public hubs in thin regional ecosystems should be evaluated not as stand-alone venues, but as part of a broader regional strategy that combines local buzz with cross-regional renewal.

\vspace{0.8em}
\noindent\textbf{Keywords:} \keywordslist

\vspace{0.35em}
\noindent\textbf{JEL classification:} \JELcodes

\vspace{1.0em}

\input{sections/01_intro}
\input{sections/02_related_literature}
\input{sections/03_model}
\input{sections/04_when_hub_efficient}
\input{sections/05_short_run_dynamic_ineff}
\input{sections/06_hub_alone_vs_refresh}
\input{sections/07_extensions}
\input{sections/08_policy_implications}
\input{sections/09_conclusion}

\section*{Data Availability Statement}
This study develops a theoretical model and does not analyze newly collected empirical data. No dataset accompanies the manuscript.

\input{sections/10_references}

\appendix
\input{appendix/appendix_proofs_4}
\input{appendix/appendix_proofs_5}
\input{appendix/appendix_proofs_6}
\input{appendix/appendix_proofs_7}

\end{document}
